Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-16 scagnostics.Rmd
formatting fix of MIC/TIC

* **information**:  The index functions [@Reshef1518] nonparametricly measure nonlinear association by computing the mutual information,

\[
\bm{I} = \sum_{by_1}\sum_{by_2} p(by_1, by_2) log(p(by_1, by_2)/(p(by_1)p{by_2})),
\]

where $by_1, by_2$ are binned values of the projected data, and $p(by_1, by_2)$ on a range of bin resolutions of the data. It is strictly a 2D measure. For a fixed binning, e.g. $2\times 2$ or $10\times 4$, the optimal binning is found by maximizing $I$. The values of I range between $[0,1]$ because they are normalized across bins by dividing by $log min(\# bins_{y_1}, \# bins_{y_2})$.

@@

    \begin{equation}
    MIC(D) = \max_{xy<B(n)}\{M(D)_{x,y}\},
    \label{eq:MIC}
    \end{equation}
    where by default $B(n) = n^{0.6}$
    see @JMLRv1715308:
    \begin{equation}
    TIC(D) = \sum_{xy<B(n)} M(D)_{x,y}
    \end{equation}
-->
    + *Maximum Information Coefficient (MIC)*: uses the maximum normalized $I$ across all bin resolutions. 
    + *Total Information Coefficient (TIC)*,: sums the normalized $I$ for all bin resolutions computed. This creates a problem of scaling - there is no upper limit, although it is related to number of bins, and number of bin resolutions used. In the work below we have made empirical estimates of the maximum and scaled the TIC index using this to get it in the range $[0,1]$. This index should be more stable than MIC.

>>>>

* **information**:  The index functions [@Reshef1518] nonparametricly measure nonlinear association by computing the mutual information, 
\begin{equation}
\bm{I} = \sum_{by_1}\sum_{by_2} p(by_1, by_2) log(p(by_1, by_2)/(p(by_1)p{by_2})),
\end{equation}
where $by_1, by_2$ are binned values of the projected data, and $p(by_1, by_2)$ on a range of bin resolutions of the data. It is strictly a 2D measure. For a fixed binning, e.g. $2\times 2$ or $10\times 4$, the optimal binning is found by maximizing $I$. The values of I range between $[0,1]$ because they are normalized across bins by dividing by $log min(\# bins_{y_1}, \# bins_{y_2})$.  
    - *Maximum Information Coefficient (MIC)*: uses the maximum normalized $I$ across all bin resolutions. 
    - *Total Information Coefficient (TIC)*: sums the normalized $I$ for all bin resolutions computed. This creates a problem of scaling - there is no upper limit, although it is related to number of bins, and number of bin resolutions used. In the work below we have made empirical estimates of the maximum and scaled the TIC index using this to get it in the range $[0,1]$. This index should be more stable than MIC.

@@

    \begin{equation}
    MIC(D) = \max_{xy<B(n)}\{M(D)_{x,y}\},
    \label{eq:MIC}
    \end{equation}
    where by default $B(n) = n^{0.6}$
    see @JMLRv1715308:
    \begin{equation}
    TIC(D) = \sum_{xy<B(n)} M(D)_{x,y}
    \end{equation}
-->
